---
title: "Explore trains"
author: "Emmanuel"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(primer.data)
```


What is the average causal effect of hearing Spanish on attitudes toward immigration among students in this class? 

Units? Students of the class
Treatments? hearing Spanish 
Outcomes? Attitude 

Preceptor Table?
A Preceptor Table is a table with rows and columns such that, if none of the data is missing, the thing we want to know is trivial to calculate.

And in our example:
we have two columns with many rows and 
one column is the ID(Students)
the other is the outcome(Attitude)
And the rows would be filled with the treatments 



Validity: is the consistency, or lack there of, in the columns of our dataset and the corresponding columns in our Preceptor Table. In order to consider the two datasets to be drawn from the same population, the columns from one must be have a valid correspondence with the columns in the other. Validity, if true (or at least reasonable), allows us to construct the Population Table.

Average Causual Effect:
The difference between one unit causal effect and other units causal effect
```{r}
trains |>
  summarise(mean_att_end = mean(att_end), .by = treatment)
```

